Title

### 2013-03-29 main.tex
added some text the the hardware introduction
added some content, but also restructured some of the folders related to hardware
added new UEM design considerations chapter
rename some sections remove "experimental results" section (unused)
clean up the introductions to the hardware and consideration sections
rather large number of tweaks to the considerations section
added compound element section (heading) and demonstration figure
Expand the model_result introduction to include a discussion of employed initial conditions.
Also moves the introduction to its own file.

\chapter{Model Results, Predictions and Implications}

In Chapters \ref{chap:previous_models} and \ref{chap:extension}, I have introduced the extended Analytic Gaussian model.
In the following chapter I use this model to make general observations about pulse propagation for Ultrafast Electron Microscopy.

@@

\chapter{Prototype Instrument}

@@

  \subimport{inc/laser/}{laser}

@@

  \subimport{inc/magnetic_lenses/}{maglens}

  \subimport{inc/hardware/}{deflector}

\chapter{Photocathode Engineering}

@@

\chapter{Experimental Results}

>>>>

\chapter{Model Results, Predictions and Implications} \label{chap:model_results}

  \subimport{inc/model_results/}{introduction}

@@

  \subimport{inc/model_results/compound/}{compound}

\chapter{UEM Design Considerations} \label{chap:considerations}

  \subimport{inc/design_considerations/}{considerations}

\chapter{Prototype Instrument} \label{chap:prototype}

@@

  \subimport{inc/hardware/laser/}{laser}

@@

  \subimport{inc/hardware/magnetic_lenses/}{maglens}

  \subimport{inc/hardware/deflector/}{deflector}

\chapter{Photocathode Engineering} \label{chap:photocathode}

@@
